---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# bigo

[![Build Status](https://travis-ci.org/bfgray3/bigo.svg?branch=master)](https://travis-ci.org/bfgray3/bigo)

`bigo` (big-O) is an R package designed to make it quick and easy to measure and visualize the runtime complexity of algorithms in your code.  It emphasizes empirical runtime measurements--in numerical values and plots--rather than theoretical complexity analysis.  This functionality is useful for researchers evaluating their algorithms, students learning computer science concepts, and many other R users.

## Installation

You can install `bigo` from GitHub.

```{r gh-installation, eval = FALSE}
# install.packages("devtools")
devtools::install_github("bfgray3/bigo")
```

## Example

Below we deomonstrate the most basic functionality of `bigo` with a simple Fibonacci function.

```{r example}
library(bigo)

fib <- function(n) {
 
  if (n < 1) {
    stop("`n` must be a positive integer.", call. = FALSE)
  } else if (n < 3) {
    return(1)
  } else {
    return(Recall(n - 1) + Recall(n - 2))
  }

}

plot(bigo(f = fib, n = seq(from = 2, to = 30, by = 2)))
```