---
title: "Introduction to bigo"
author: "Bernie Gray"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Complexity of finding missing values

In this vignette we'll explore the `bigo` package by comparing the built-in `anyNA` with the user-defined `function(x) any(is.na(x))`.  According to `?anyNA`, "The generic function `anyNA` implements `any(is.na(x))` in a possibly faster way (especially for atomic vectors)."

## Setup

Below we set up the functions that we'll use in our benchmarking. `fast` and `slow` take one argument, `n`, which is the parameter we will evaluate for runtime complexity.

```{r}
library(bigo)

set.seed(4444)
N <- c(NA, rnorm(1e8))
my_anyNA <- function(x) any(is.na(x))

benchmark_maker <- function(fun) {
  
  function(n) {
    x <- N[seq_len(n)]
    fun(x)
  }
  
}

fast <- benchmark_maker(fun = anyNA)
slow <- benchmark_maker(fun = my_anyNA)
```

## Complexity analysis

We use `bigo::bigo` to conduct our analysis, measuring runtime on 10 evenly spaced values of `n` from `1e6` to `1e8`.

```{r}
complexity_grid <- 10 ^ seq(from = 6, to = 8, length.out = 10)
(fast_bigo <- bigo(f = fast, n = complexity_grid))
(slow_bigo <- bigo(f = slow, n = complexity_grid))
```

Notice that the objects have class `bigo` and have three elements: `runtimes`, `function_name`, and `num_runs`.

```{r}
class(fast_bigo)
names(fast_bigo)
```

Let's plot these runtimes to get a sense for the general shape of the runtime growth.  `bigo` provides an S3 `plot` method.

```{r}
plot(fast_bigo)
plot(slow_bigo)
```

In this region, both plots look relatively linear, with the `fast` plot having lower runtime values in general.  OLS on each of these datasets gives the following results.

```{r}
fast_df <- fast_bigo[["runtimes"]]
slow_df <- slow_bigo[["runtimes"]]

lm(elapsed ~ n, data = fast_df) # anyNA
lm(elapsed ~ n, data = slow_df) # my_anyNA
```

For the built-in `anyNA`, we do observe a smaller slope, i.e. the user-defined function does scale more poorly as `n` grows (although only by a multiplicative constant).  Let's see how this difference evolves over time.

```{r}
suppressPackageStartupMessages(library(dplyr))
suppressPackageStartupMessages(library(ggplot2))

slow_df %>%
  inner_join(fast_df, by = "n", suffix = c("_slow", "_fast")) %>%
  mutate(difference = elapsed_slow - elapsed_fast) %>%
  ggplot(aes(x = n, y = difference)) +
    geom_line() +
    labs(title = "Runtime difference",
         subtitle = "my_anyNA - anyNA",
         y = "Difference (s)")
```

The underperformance of `my_anyNA` generally worsens as `n` increases, due to the smaller slope of `anyNA`.